```{r data generation, echo = FALSE, results = 'hide'}
## DATA GENERATION
library(forecast)
```

Question
========

Match ACF and PACF with their corresponding ARMA processes: 

```{r, echo = FALSE}

set.seed(666)

a = arima.sim(n = 1000, list(ar = c(0.5, 0.3), ma = c(0.8, 0.7)),
          sd = sqrt(0.1))

par(mfrow = c(1, 2))
acf(a, lag.max = 20)
pacf(a, lag.max = 20)
par(mfrow = c(1, 1))



b = arima.sim(n = 1000, list(ar = c(0.5, 0.3)),
          sd = sqrt(0.1))

par(mfrow = c(1, 2))
acf(b, lag.max = 20)
pacf(b, lag.max = 20)
par(mfrow = c(1, 1))



c = arima.sim(n = 1000, list(ma = c(0.7, -0.5)),  sd = sqrt(0.1))


par(mfrow = c(1, 2))
acf(c, lag.max = 20)
pacf(c, lag.max = 20)
par(mfrow = c(1, 1))


d = arima.sim(n = 1000, list(ar = c(-0.8)), sd = sqrt(0.1))


par(mfrow = c(1, 2))
acf(d, lag.max = 20)
pacf(d, lag.max = 20)
par(mfrow = c(1, 1))




```




1. ARMA(2,0)

2. ARMA(1,0)

3. ARMA(0,2)

4. ARMA(2,2) 





Write down in the solution the sequence of numbers without spaces or delimeters corresponding to pairs of ACF and PACF in each case (e.g. 4231).

Solution
========

A gradual geometrically declining ACF and a PACF that is significant for only a few lags indicate an AR process. MA process shows a gradually geometrically declining PACF and the ACF has a few significant lags. An ARMA process is indicated by geometrically filling ACF and PACF. 


Meta-information
================
exname: ARMA - plots
extype: num
exsolution: 4132
extol: 0
	