```{r data generation, echo = FALSE, results = 'hide'}
## DATA GENERATION

library(forecast)
options(scipen=999)

```

Question
========

Consider LakeHuron time series.

You can load the LakeHuron data set in R by issuing the following command at the console data("LakeHuron") or if you use other programming languages you can download it [here](https://github.com/vincentarelbundock/Rdatasets/blob/master/csv/datasets/LakeHuron.csv).


```{r, echo = FALSE}

ggtsdisplay(LakeHuron)

```



By analysing ACF and PACF functions answer, what can the underlying ARMA(p,q) process be?




Answerlist
----------

*  ARMA(0,0)
*  ARMA(1,0)
*  ARMA(2,0)
*  ARMA(0,1)
*  ARMA(0,2)
*  ARMA(1,1)


Solution
========

A gradual geometrically declining ACF and with  PACF  that is significant for only  2 lags indicate an AR process. Since the number of observations is not large enough the significance of PACF(2) is questionable.




Meta-information
================
exname: stat cond
extype: mchoice
exsolution: 011000
exshuffle: 6

