```{r data generation, echo = FALSE, results = 'hide'}
## DATA GENERATION

library(forecast)
options(scipen=999)

```

Question
========

Let's continue conducting a Box-Jenkins procedure for log(gas) time series. 


You can load the gas dataset in R by importing forecast library or if you use other programming languages you can download it [here](https://github.com/vincentarelbundock/Rdatasets/blob/master/csv/forecast/gas.csv).



```{r, echo = FALSE}
ggtsdisplay(log(gas))

```

Is the process stationary?




Answerlist
----------
* Yes, we can proceed with log(gas) time series
* No, first differencing should be applied
* No, seasonal differencing should be applied
* No, both first and seasonal differencing should be applied


Solution
========

Only if we apply both first and seasonal differences the mean will be stable over time. From analysing the ACF plot it is clear that there is a unit root and a seasonal unit root, but you can also check this using unit root tests. 


Meta-information
================
exname: bj 
extype: schoice
exsolution: 0001
exshuffle: 4

