```{r data generation, echo = FALSE, results = 'hide'}
## DATA GENERATION

library(forecast)
options(scipen=999)

```

Question
========

Let's continue conducting a Box-Jenkins procedure for the differenced log(gas) time series. 


You can load the gas dataset in R by importing forecast library or if you use other programming languages you can download it [here](https://github.com/vincentarelbundock/Rdatasets/blob/master/csv/forecast/gas.csv).




```{r, echo = FALSE}
ggtsdisplay(diff(diff(log(gas)),12), lag.max = 48)

```

Now let's determine the parameters for SARIMA model.

By analysing ACF and PACF functions answer, what can the underlying SARMA(p,q) process for the transformed and differenced gas series be?


Answerlist
----------
* SARMA(0,0)[0,1]
* SARMA(0,1)[0,0]
* SARMA(0,1)[0,1]
* SARMA(1,0)[0,0]
* SARMA(0,0)[1,0]
* SARMA(1,0)[1,0]


Solution
========

MA process shows a gradually declining PACF and the ACF has a 1st significant lag corresponding to MA part and 12th significant lag corresponding to seasonal MA part. 




Meta-information
================
exname: bj 
extype: schoice
exsolution: 001000
exshuffle: 6

