```{r data generation, echo = FALSE, results = 'hide'}
## DATA GENERATION
library(forecast)
library(ggplot2)
library(patchwork)
```

Question
========

Consider the following time series on Australian monthly gas production: 

```{r, echo = FALSE}
autoplot(gas)
```

We have applied Box-Cox transformation with different parameters:

```{r, echo = FALSE}

A = BoxCox(gas,1)
B = BoxCox(gas,0)
C = BoxCox(gas,0.5)
D = BoxCox(gas,-2)

(autoplot(A)/autoplot(B)/autoplot(C)/autoplot(D))
```

1. $\lambda=-2$

2. $\lambda=0$

3. $\lambda=1$

4. $\lambda=0.5$

Write down in the solution the sequence of numbers without spaces or delimeters corresponding to parameters of Box-Cox transformation $\lambda_A,\lambda_B,\lambda_C,\lambda_D$ applied in each case (e.g. 4231).

Solution
========

Suppose $y^{bc}$ is transformed data. If $\lambda=0$, the transformation is equivalent to $y^{bc}=\ln(y)$, if $\lambda=1$ it's $y^{bc}=y$, if $\lambda=0.5$ it's $y^{bc}=\sqrt{y}$,  if $\lambda=-2$ it's $y^{bc}=y^{-2}$.

Meta-information
================
exname: Series Components - Box-Cox lambda
extype: num
exsolution: 3241
extol: 0
	